A tool set for random number generation on GPUs in R

### 2022-01-08 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
update paper 1, ref timenumber anistr
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3102 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{A summary of the results}
We summarized the comparison results in Table \ref{tab:summary} and plot the test statistics in Figure \ref{fig4}.
<<summarycompare, echo=FALSE, eval=TRUE, cache=TRUE,fig.pos='H'>>=
library(kableExtra)
dt <- data.frame(
  var1 = c("B", "1M", "10M", "1M", "10M"),
  var2 = c('Intel 2.5ghz', 0.403804, 0.0001251, 10.74,  63.24),
  var3 = c('AMD Radeon', 0.403507, 0.0001274,   2.28,    10.82),
  var4 = c('Intel 3.7ghz', 0.4035606,0.0001202, 14.80,  92.00),
  var5 = c('NVIDIA V100', 0.403507,0.0001274,   0.32,   1.95),
  var6 = c('Data','month','week','month','week')
)

@@

GEOMETRIC ANISOTROPY

>>>>

\subsection{A summary of the results}
We summarized the comparison results in Table \ref{tab:summary} and plot the test statistics in Figure \ref{fig4}.
<<summarycompare, echo=FALSE, eval=TRUE, cache=TRUE,fig.pos='H'>>=
library(kableExtra)
dt <- data.frame(
  var1 = c("B", "1M", "10M", "1M", "10M"),
  var2 = c('Intel 2.5ghz', 0.403804, 0.0001251, 49.33,  327.27),
  var3 = c('AMD Radeon', 0.403507, 0.0001274,   2.15,    10.23),
  var4 = c('Intel 3.7ghz', 0.4035606,0.0001202, 14.80,  92.00),
  var5 = c('NVIDIA V100', 0.403507,0.0001274,   0.32,   1.95),
  var6 = c('Data','month','week','month','week')
)

@@

GEOMETRIC ANISOTROPY
Geometrical anisotropy is defined by two additional parameters in the correlation function. Let $(x_1, x_2)$ represent the original coordinates, which is rotated counterclockwise by $\varphi$, then the new coordinates $(x'_1, x'_2)$ is given by
%
  \begin{equation*}\label{eq:matrixeqn}
    \begin{pmatrix}
      x'_{1} \\
      x'_{2}  
    \end{pmatrix}
    =
    \begin{pmatrix}
      1/\phi_{1} & 0 \\
      0 & 1/ \phi_{2} 
    \end{pmatrix}
    \cdot
    \begin{pmatrix}
      \cos \varphi & -\sin \varphi \\
      \sin \varphi & \cos \varphi 
    \end{pmatrix}
    \cdot
      \begin{pmatrix}
      x_1 \\
      x_2 
    \end{pmatrix},
  \end{equation*}
